Towards Verifying the Bitcoin-S Library

### 2019-06-24 paper/paper.tex
add appendix
move transformations to appendix

\subsection{Fixing a Bug in Bitcoin-S}
\label{sec:bugfix}

@@

\subsection{Adjusting No-Inflation Property}

\todo{Kai: check the text

In order to verify a project, Stainless must be integrated into it.
We can integrate it in an sbt project adding the Stainless Plugin 
and the required resolver to pugins.sbt. 
Another option to use Stainless is to import its libraries in a program code 
and verify a program from command line using the pre-packaged Stainless JAR file 
or using the Stainless script built from source.}
Trying to integrate Stainless in Bitcoin-S caused a lot of troubles,
mainly because of version conflicts.  For more details see chapter
\ref{chap:appendix_arb}.

The extracted code has more than 1500 lines.  After running Stainless
on it, it still throws a huge bunch of errors about what Stainless can
not reason about. After fixing some of those errors, there appear new
ones.  So this would require changing nearly everything of the
extracted code.

So let's look at the \nameref{property_2}.

@@

>>>>

\paragraph{Stainless integration problems.}

\todo{Kai: check the text}

In order to verify a project, Stainless must be integrated into it.
We can integrate it in an sbt project adding the Stainless Plugin 
and the required resolver to pugins.sbt. 
Another option to use Stainless is to import its libraries in a program code 
and verify a program from command line using the pre-packaged Stainless JAR file 
or using the Stainless script built from source.
Trying to integrate Stainless in Bitcoin-S caused a lot of troubles,
mainly because of version conflicts.  For more details see chapter
\ref{chap:appendix_arb}.

\paragraph{Extracting the relevant code.}
The extracted code has more than 1500 lines.  After running Stainless
on it, it still throws a huge bunch of errors about what Stainless can
not reason about. After fixing some of those errors, there appear new
ones.  So this would require changing nearly everything of the
extracted code.

\paragraph{Fixing a Bug in Bitcoin-S}

@@

@@

When we run Stainless on this code (without any properties to prove), it throws the following errors: \todo{describe errors: no support for abstract types, unsupported arguments for the BigInt constructor, unsupported inheritance for objects.}

\appendix
\section{Code Transformations}

\paragraph{Project Setup}
\begin{itemize}
\item clone our repo
\item contains a stainless jar
\item call the script blahblah
\end{itemize}
